%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                 %
%                            CHAPTER TWO                          %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{RELATED WORKS} \label{sec:introduction}
% Remeber, this is what we have: 
% 	Sketching, Early Design, Daylighting, Web, User Study
The need for daylighting analysis earlier in the architectural design process, drives the development of tools that generate timely results at affordable levels of effort.
In order to perform daylighting analysis, these tools must either import or generate 3D models of architectural spaces.
Some tools come packaged with their own parametric or geometric modeling capabilities, however, other tools are available as plug-ins for existing geometric modeling software.
Moreover, there are handful of daylighting analysis tools that use sketching inspired interfaces for generating 3D models.
All of the analysis tools mentioned below face similar challenges.
These tools attempt to provide a means to perform daylighting analysis earlier in the architectural design process.

\section{Early Design Phase Parametric-Modeling Daylighting Tools}

	Some early design tools such as HEED and eQUEST allow users to defined architectural spaces with parametric-modeling interfaces. 
	Parametric modeling, as seen in HEED and eQUEST, is the creation of architectural models by defining a set finite parameters.
	These parameters, such as room dimensions, define an architectural space.
	In order to manage the large number of parameters required to analyze energy consumption of a space, both HEED and eQuest use wizards to guide users along the complex processes of defining an architectural space.


	
	Remarkably, for eQUEST 41 pages of parameters must be defined before conducting analysis on a space given a full 3D model.
	However, parametric modeling doesn't offer much flexibility in design of models.
	HEED and eQUEST are both early design tools that provide users with energy design analytical tools -- including daylighting.
	But because the tools cannot create 
	These tools provide only quantitative data to architects, and do not produce rendering.



	%\subsection{HEED}

	%\subsection{eQUEST}

\section{Early Desing Phase Geometric-Modeling Daylighting Tools}
	%\subsection{Sketchup with Lightsolve}
	%\subsection{Autodesk with Ecotect}
	%\subsection{Rhino with Ladybug}
	%\subsection{Velux}
	%\subsection{Daylight-1-2-3}

\section{Early Design Phase Sketch-Modeling Daylighting Tools}
	%\subsection{Light Sketch}
	%\subsection{Virtual Heliodon}
